---
title: "Homework 5 413"
author: "Mahima Palamanda"
date: "3/2/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
Stockreturns <- c(-8.36, 1.63, -2.27, -2.93, -2.70,
-2.93, -9.14, -2.64, 6.82, -2.35,
-3.58, 6.13, 7.00, -15.25, -8.66,
-1.03, -9.16, -1.25, -1.22, -10.27,
-5.11, -0.80, -1.44, 1.28, -0.65,
4.34, 12.22, -7.21, -0.09, 7.34,
5.04, -7.24, -2.14, -1.01, -1.41,
12.03, -2.53, 4.33, 1.35)
Stockreturns
```
```{r}
#Question 1
mean(Stockreturns)
```
```{r}
#Question 2
sd(Stockreturns)
```
```{r}
#Question 3
pnorm(-1.5, -1.124615,5.977673)
```
47.5% are less than -1.5 assuming normal distribution 
```{r}
#Question 4
qnorm(.7,-1.124615,5.977673)
```
70% of them were below the 2% return
```{r}
#Question 5
qnorm(.25,-1.124615,5.977673)#using the normal assumption
quantile(Stockreturns,probs=.25)#using data 
```
```{r}
#Question 6
ggplot(mapping = aes(y=Stockreturns))+
  geom_boxplot()
ggplot(mapping=aes(sample=Stockreturns))+stat_qq()
```
The data is approximately normal. The boxplot looks symmetric. The QQ plot came out to be a straight line.  

#Question 7
mu is the average return of the population the sample came from. 
h0: mu is greater than or equal to 0.95%
ha: mu is less than 0.95%
if it rejects, then we can conclude that this is less than average

```{r}
#Question 8
t.test(Stockreturns,alternative="less",mu=.95)#one-tail
```
The p value is 0.01827. 
The confidence interval is -inf to .4891698

#Question 9
In conclusion, the broker is performing at less than average. At a 5% level of significance, we can reject the null hypothesis. The upper end of the confidence level is less than .95% which means we can reject the null hypothesis. 
